### 2017-06-01 src/mstats3.tex
Changed wording in example.
Added proof of E(S^2) = sigma^2.
Added estimation and hypothesis section.

\section{Estimators}
    \paragraph{Sample Statistic} A function of observed data, used to estimate parameters (such as mean and varience).

@@

    $\dfrac{4}{3} > 1$ so $\hat{P}_1$ is the best estimate for parameter $p$.

@@

\section{Estimation}
\section{Hypothesis Testing}
\section{Chi-Squared ($\chi^2$) Goodness of Fit Testing}

>>>>

\section{Estimators}
    \subsection{Estimators, Unbiased, consistent and efficiency}
        \paragraph{Sample Statistic} A function of observed data, used to estimate parameters (such as mean and varience).

@@

        $\dfrac{4}{3} > 1$ so $\hat{P}_1$ is the more efficent.

@@

    \subsection{Proof of $E(S^2) = \sigma^2$}
        Using these methods, we can now prove $E(S^2) = \sigma^2$
        \begin{align*}
            \bar{X}  &= \sum{\dfrac{X_i}{n}} \\
            n\bar{X} &= \sum{X_i}\\\\
            \dfrac{\sigma^2}{n} &= E(\bar{X}^2) - \mu^2 \\
            E(\bar{X}^2) &= \dfrac{\sigma^2}{n} + \mu^2
        \\\\
        E(S^2) &= E\left(\dfrac{1}{n-1} \times \sum{(X_i - \bar{X})^2}\right)               \\
            &= \dfrac{1}{n-1} \times E\left(\sum{(X_i - \bar{X})^2}\right)               \\
            &= \dfrac{1}{n-1} \times \sum{E((X_i - \bar{X})^2)}                          \\
            &= \dfrac{1}{n-1} \times \sum{E(X_i^2 - 2\bar{X}X_i + \bar{X}^2)}            \\
            &= \dfrac{1}{n-1} \times \sum{(E(X_i^2) - E(2\bar{X}X_i) + E(\bar{X}^2))}    \\
            &= \dfrac{1}{n-1} \times \left(\sum{E(X_i^2)} - \sum{E(2\bar{X}X_i)} + \sum{E(\bar{X}^2))}\right) \\
            &= \dfrac{1}{n-1} \times \left(n(\sigma^2 - \mu^2) - E\left(\sum{2\bar{X}X_i}\right) + E\left(\sum{\bar{X}^2}\right)\right)\\
            &= \dfrac{1}{n-1} \times \left(n(\sigma^2 - \mu^2) - E\left(2\bar{X} \times n\bar{X}\right) + E\left(n\bar{X}^2\right)\right)\\
            &= \dfrac{1}{n-1} \times \left(n(\sigma^2 - \mu^2) - E\left(2n\bar{X}^2\right) + E\left(n\bar{X}^2\right)\right)\\
            &= \dfrac{1}{n-1} \times \left(n(\sigma^2 - \mu^2) - E\left(n\bar{X}^2\right)\right)\\
            &= \dfrac{1}{n-1} \times \left(n(\sigma^2 - \mu^2) - nE\left(\bar{X}^2\right)\right)\\
            &= \dfrac{1}{n-1} \times \left(n(\sigma^2 - \mu^2) - n\left(\dfrac{\sigma^2}{n} + \mu^2\right)\right)\\
            &= \dfrac{1}{n-1} \times (n\sigma^2 - n\mu^2 - \sigma^2 + n\mu^2)\\
            &= \dfrac{1}{n-1} \times (n\sigma^2 - \sigma^2)\\
            &= \dfrac{1}{n-1} \times \sigma^2(n-1)\\
            &= \sigma^2
        \end{align*}

\section{Estimation}
    \subsection{Confidence interval for diffrence in means of two normal distributions}
        The confidence interval for the diffrence of two means is as simple as finding the diffrence between the two sets of samples and finding the confidence interval as normal.

        \begin{example}
        {
            The following is the blood pressure of patients while sitting and standing.

            \begin{center}
            \begin{tabular}{l|c|c|c|c|c|c|c|c|c|c|c|c}
                Patient     & A & B & C & D & E & F & G & H & I & J & K & L \\
                \hline
                Sitting     & 72 & 79 & 69 & 76 & 82 & 66 & 87 & 78 & 85 & 77 & 84 & 70 \\
                Standing    & 81 & 70 & 79 & 84 & 88 & 77 & 79 & 85 & 91 & 74 & 88 & 80 
            \end{tabular}
            \end{center}

            Construct a 95\% confidence inteval for the mean diffrence between the patient's blood pressure assuming the diffrence in blood pressure are normally distributed, and state weather the claim that patients blood pressure are diffrent is supported.
        }

        \begin{step}{Find the diffrence}
            $$
                d_i = 9, -9, 10, 8, 6, 11, -8, 7, 6, -3, 4, 10
            $$
        \end{step}

        \begin{step}{Find the mean and variance of the diffrences}
            $$
                \bar{d} = 4.5
            $$
            $$
                s_d = 7.01
            $$
        \end{step}

        \begin{step}{Find the critical value}
            $$
                cv = t_{11} = 2.201
            $$
        \end{step}

        \begin{step}{Construct the confindence inteval}
            \begin{align*}
                4.25 \pm 2.201 \times \dfrac{7.01}{\sqrt{12}} &= (-0.20, 8.70)
            \end{align*}
        \end{step}

        \begin{step}{Conclude}
            The confindence interval includes 0, so their is no evidence to support the claim that patients blood pressure is diffrent between sitting and standing.
        \end{step}

    \subsection{Confindence interval for variance}
        (See SS05 Confindence interval for variance)

    \subsection{Confindence interval for the ratio of two variances}
         The ratio of variances is used it ANOVA and variance test's, but we can also find its confindence interval.

         Given $s_x$, $n_x$, $s_y$ and $n_y$ of two normal distributions, the confidence interval for the ratio of the variances is as follows:
         $$
         \dfrac{1}{F_{v_1, v_2}} \leq \frac{VR}{F_{\text{calc}}} \leq F_{v_2, v_1}
         $$
         Where $F_{\text{calc}} = \dfrac{s_x^2}{s_y^2}$, $v_1 = n_x - 1$ and $v_2 = n_y - 1$

         \begin{example}
         {
             The broadband speed of 12 rural villages are as follows:
             $$1.9, 2.6, 1.8, 3.4, 2.2, 3.0, 2.7, 3.7, 2.7, 1.9, 3.4, 3.1$$
             The broadband speed of 9 small towns are as follows:
             $$7.8, 7.7, 7.5, 7.7, 8.0, 7.3, 7.7, 7.4, 7.8$$

             Determine a 99\% confindence interval for the variance ratio $\dfrac{\sigma_X^2}{\sigma_Y^2}$, and comment on the suggestion that rutal villages is more variable than small towns.
         }

         \begin{step}{Find the variance of $X$ and $Y$}
            $$s_X^2 = 0.41636$$
            $$s_Y^2 = 0.04778$$
         \end{step}

         \begin{step}{Find the critical values}
            \begin{align*}
            v_1       &= 12 - 1   \\
                      &= 11       \\
            v_2       &= 9 - 1    \\
                      &= 8        \\
            F_{11, 8} &= 7.104    \\
            F_{8, 11} &= 5.682
            \end{align*}
            $$\dfrac{1}{7.104} \leq \dfrac{VR}{8.7146} \leq 7.682$$
            $$1.23 \leq VR \leq 49.5$$
         \end{step}

         \begin{step}{Conclude}
            1 is not inside the confidence interval, so broadband speeds are more varible in villages.
         \end{step}

\section{Hypothesis Testing}
    \subsection{Test for diffrence between in mean}
        (See SS5 Test for diffrence between in mean)

    \subsection{Tests for a variance}
        (See SS5 Test for variance equality)

    \subsection{Test for the ratio of two variances}
        Much like how we can test for variace equality, we can test the ratio of two variances in a simular mannor.

        \subsubsection{Process}
            \begin{enumerate}
            \item Hypothesis.
            \item Find the sample variances
            \item Calculate the $F_{\text{test}}$ divided by the ratio that we assume in $H_0$
            \item Determine the critical value
            \item Conclude
            \end{enumerate}

        \begin{example}
        {
            With the following data:
            \begin{center}
            \begin{tabular}{c|c|c}
            Distribution & $s^2$ & $n$ \\
            $S$ & 3372.75 & 12 \\
            $N$ & 290.5 & 8 \\
            \end{tabular}
            \end{center}
            Test the claim that the standard deviation of $S$ is twice that of $N$.
        }

        \begin{step}{Hypothesis}
            $$ H_0: \sigma_S = 2 \sigma_N $$
            $$ H_0: \sigma_S \ne 2 \sigma_N $$
        \end{step}

        \begin{step}{Sample variances}
            $$s_S^2 = 3372.75$$
            $$s_N^2 = 290.5$$
        \end{step}

        \begin{step}{Calculate $F_\text{test}$}
            \begin{align*}
                F_\text{test} &= \dfrac{3372.75}{2^2 \times 290.5}  \\
                              &= 2.90
            \end{align*}
        \end{step}

        \begin{step}{Critical value}
            \begin{align*}
            v_1 &= 12 - 1       \\
                &= 11           \\
            v_2 &= 8 - 1        \\
                &= 7            \\\\
            F_{11, 7} &= 3.60
            \end{align*}
        \end{step}

        \begin{step}{Conclude}
            $2.80 < 3.60$, so accept $H_0$ significant evidence that the standard deviation of $S$ is twice that of $N$.
        \end{step}

\section{Chi-Squared ($\chi^2$) Goodness of Fit Testing}
